Top-down Segment-based Neuron Reconstruction

### 2017-11-13 papers/cvpr2018/0_introduction.tex
Changed sections 1 and 2 and some other errors such as duplicate bibtex.

The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions. 
Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) has allowed neuroscientists to produce terabytes of electron micrsocopy (EM) image data every hour~\cite{hildebrand2017whole}.
Neuroscientists believe that reconstructing an entire mammalian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated}. 
These observations will allow for new advancements in neuromedicine and artificial intelligence.

Segmenting the image stack into a label volume is a substantial component of this reconstruction process.
In a label volume, every voxel receives a segment label corresponding to a unique neuron. 
Voxels with the same label belong to the same neuron.
It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain.
Here we introduce a scalable, top-down segmentation algorithm that also leverages local information.
Partitioning from a top-down approach allows us to apply domain-specific constraints to the segmentation task.

@@

\begin{figure*}[h!]
	\centering
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/image.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/affinities.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/watershed.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/neuroproof.png}
	\caption{An overview of an existing pipeline in segmentation for connectomics. From left to right: the original EM image data, the output of a CNN predicting voxel affinities, clustering of the affinities using a watershed algorithm, an agglomeration of the supervoxels into larger segments.}
	\label{fig:pipeline}
\end{figure*}

@@

We present a \textit{segment-based} strategy that builds on the outputs of region-based methods (Figure \ref{fig:teaser}).
We only take as input a segmentation from the region-based agglomeration algorithm. 
This allows us to train on connectomics datasets at a given resolution and image type and test on another resolution.
This is a huge plus considering the sheer amount of expert-hours needed to generate ground truth for these massive datasets.
We extract a graph representation from the input segmentation.
By simplifying the 3-D segments by their skeletons, we can quickly generate the graph nodes and edges. 
We train a 3-D CNN to populate the graph edge weights with bottom-up local information. 
We enforce domain-specific global constraints, such as the underlying biology, using a graph-based partitioning heuristic.
In this we can leverage both local and global information to produce a more accurate segmentation.

Our novel approach creates a level of abstraction over existing region-based agglomeration strategies. 
We take the output of these methods as input and extract a graph structure from that.
This allows us to enforce restrictions on our output that closely follow the underlying biology of these connectomics datasets. 
We use bottom-up information to weight the edges in our graph and top-down information when partitioning the graph. 
This dual approach of assessing local decisions in a global framework produces improvements over the existing region-based methods.

>>>>

The field of connectomics is concerned with reconstructing the wiring diagram of the brain at nanometer resolutions. 
Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) has allowed researchers to produce terabytes of electron microscopy (EM) image data every hour~\cite{hildebrand2017whole}.
Neuroscientists believe that reconstructing an entire mammalian brain at fine resolution will enable new insights into the workings of the brain~\cite{kasthuri2015saturated,haehn2017scalable}. 
These observations will allow for new advancements in neuromedicine and artificial intelligence.

Segmenting the image stack into a label volume is a substantial component of this reconstruction process.
In a label volume, every voxel receives a segment label corresponding to a unique neuron. 
Voxels with the same label belong to the same neuron.
It is not feasible for domain experts to manually segment the vast amount of 3-D image data to model an entire brain~\cite{haehn2014design}.
Here we introduce a scalable, top-down segmentation algorithm that also leverages local information.
Partitioning globally allows us to apply domain-specific constraints to the segmentation task.

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/image.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/affinities.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/watershed.png}
	\hspace{0.025\linewidth}
	\includegraphics[width=0.22\linewidth]{./figures/pipeline/neuroproof.png}
	\caption{An overview of an existing pipeline in segmentation for connectomics. From left to right: the original EM image data, the output of a CNN predicting voxel affinities, clustering of the affinities using a watershed algorithm, an agglomeration of the supervoxels into larger segments.}
	\label{fig:pipeline}
\end{figure*}

@@

@@

We present a \textit{segment-based} strategy that builds on the outputs of region-based methods (Figure \ref{fig:teaser}).
For training a classifier based on a CNN, we only take as input the segmentation from a region-based agglomeration algorithm. 
This renders our classifier independent of image resolution and characteristics such as anisotropy and for instance, allows the application to isotropic data without retraining.
This is a huge plus considering the sheer amount of expert-hours needed to generate ground truth for these massive datasets.
We extract a graph representation from the input segmentation.
By simplifying the 3-D segments by their skeletons, we can quickly generate the graph nodes and edges. 
We train a 3-D CNN to populate the graph edge weights with bottom-up local information. 
We enforce domain-specific global constraints, such as the underlying biology, using a graph-based partitioning heuristic.
In this we can leverage both local and global information to produce a more accurate segmentation.

Our approach creates a level of abstraction over existing region-based agglomeration strategies. 
We take the output of these methods as input and extract a graph structure from that.
This allows us to enforce global restrictions on our output that closely follow the underlying biology of these connectomics datasets such as limiting the allowed angles of neuron branching. 
In addition we use local information such as shape priors to weight the edges in our graph.
This dual approach of assessing local decisions in a global framework produces improvements over the existing region-based methods.

### 2017-11-13 papers/cvpr2018/1_related_work.tex
Changed sections 1 and 2 and some other errors such as duplicate bibtex.

A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images to produce label volumes.
Some early techniques apply computationally expensive graph partitioning algorithms with a single node per voxel~\cite{andres2012globally}, however these methods do not scale to terabyte datasets.
Since then, several methods train 2-D CNNs to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,rhoananet,amelio_segmentation}. 
More recent strategies augment these neural networks with the $z$-dimension creating full 3-D CNNs~\cite{lee2015recursive,ronneberger2015u}.
Oftentimes these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron).
The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}. 
More recently, flood-filling networks produce segmentations by training an end-to-end neural network that takes EM images to label volumes~\cite{januszewski2016flood}.
These flood-filling networks produce very impressive accuracies but at too high a computational cost.

>>>>

A large amount of connectomics research considers the problem of extracting segmentation information at the voxel level from the raw EM images to produce label volumes.
Some early techniques apply computationally expensive graph partitioning algorithms with a single node per voxel~\cite{andres2012globally}, however these methods do not scale to terabyte datasets.
Since then, several methods train 2-D CNNs to predict membrane probabilities per image slice~\cite{ciresan2012deep,jain2010boundary,kaynig2015large,seymour2016rhoananet,amelio_segmentation}. 
More recent strategies augment these neural networks with the $z$-dimension creating full 3-D CNNs~\cite{lee2015recursive,ronneberger2015u}.
Oftentimes these networks produce probabilities for the affinity between two voxels (i.e., the probability that adjacent voxels belong to the same neuron).
The MALIS cost function is specifically designed for generating affinities that produce good segmentations~\cite{briggman2009maximin}. 
More recently, flood-filling networks produce segmentations by training an end-to-end neural network that takes EM images to label volumes~\cite{januszewski2016flood}.
These flood-filling networks produce very impressive accuracies but at a high computational cost.

### 2017-11-13 papers/cvpr2018/paper.tex
paper: updated entire paper
Changed sections 1 and 2 and some other errors such as duplicate bibtex.

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algpseudocode}
\usepackage{algorithmicx}
\usepackage{siunitx}
\usepackage{float}

@@

%%%%%%%%% TITLE
\title{Graph-based Neuron Agglomeration using 3D Skeletons}

@@

\begin{figure}[t]\footnotesize
	\vspace{-2.04in}
	\begin{minipage}{\textwidth}
		\begin{minipage}{0.125\textheight}
			\includegraphics[width=\linewidth]{figures/schema/teaser-image.png}
			\includegraphics[width=\linewidth]{figures/schema/teaser-segmentation.png}
		\end{minipage}
		\begin{minipage}{0.24\textwidth}
			\includegraphics[width=\linewidth]{figures/schema/pre-multicut.png}
		\end{minipage}
		\begin{minipage}{0.34\textwidth}
			\includegraphics[width=\linewidth]{figures/schema/multicut-graph.png}
		\end{minipage}
		\begin{minipage}{0.24\textwidth}
			\includegraphics[width=\linewidth]{figures/schema/post-multicut.png}
		\end{minipage}
		\caption{We take as input the results of a region-based agglomeration algorithm. We extract a graph from this segmentation and apply a top-down partitioning algorithm to improve accuracy.}
		\label{fig:teaser}
	\end{minipage}
\end{figure}

>>>>

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{siunitx}
\usepackage{float}

@@

%%%%%%%%% TITLE
\title{Top-down Segment-based Neuron Reconstruction}

@@

\begin{figure}[t]\footnotesize
	\vspace{-2.04in}
	\begin{minipage}{\textwidth}
		\begin{minipage}{0.125\textheight}
			\includegraphics[width=\linewidth]{figures/schema/teaser-image.png}
			\includegraphics[width=\linewidth]{figures/schema/teaser-segmentation.png}
		\end{minipage}
		\begin{minipage}{0.24\textwidth}
			\includegraphics[width=\linewidth]{figures/schema/pre-multicut.png}
		\end{minipage}
		\begin{minipage}{0.34\textwidth}
			\includegraphics[width=\linewidth]{figures/schema/multicut-graph.png}
		\end{minipage}
		\begin{minipage}{0.24\textwidth}
			\includegraphics[width=\linewidth]{figures/schema/post-multicut.png}
		\end{minipage}
		\caption{To reconstruct neurons, we take as input the results of a region-based agglomeration algorithm. We extract a graph from this segmentation and apply a partitioning algorithm with local and global features to improve accuracy.}
		\label{fig:teaser}
	\end{minipage}
\end{figure}
